The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-23 paper/ms.tex
equations
addition to paper chemical part with new plots

\begin{equation}
\label{scaling}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
\end{equation}

@@

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} (\dfrac{R}{\rsun})^{-3}}
\end{equation}

@@

Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above. Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive. The spectra generated will have different [X/Fe] values. A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for a given element. To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

\subsubsection{Chemical Composition}
\label{chemical}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

>>>>

\begin{equation}
\label{scaling}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}}
\end{equation}

@@

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} \left(\dfrac{R}{\rsun}\right)^{-3}}
\end{equation}

@@

Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above. Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive. The spectra generated will have different [X/Fe] values. A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for a given element. { \bf Ben: Maybe remove this if we do not actually implement line-by-line differential; Do we have a TRES Arcturus spectrum.} Abundance uncertainties reported are the standard error in the line-by-line abundance ratios. Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex. In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising from incorrect line list data upon other things. We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}. To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn from. The first thing to note is that the metallicity, which are tabulated in Table~\ref{stellar_props}, are to high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around --1.20 \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces). We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}. } 
\end{figure*}
The $\alpha$ elements are thought to form in  variety ways during internal fusion within a star while it evolves over its life. These elements are then largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. The most important of these diagrams are those including the abundances of the $\alpha$ elements as a function of metallicity. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{We note that there are likely systematics between our [X/Fe] abundance scale and those of our comparison samples. We do not have the relevant data, which include several stars in common with these studies but observed with the TRES spectrograph, to asses the level of systematics.}  to representative disk stars from \cite[open red square,][]{Bensby2014} and \cite[open orange triangles,][]{Adibekyan2012}.

For most of the stars in our sample, the [Mg, Ti, Ca/Fe] abundance ratios are enhanced. The commonly used [$\alpha$/Fe] abundance ratio is the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4.0) ) is also enhanced in most stars. This is consistent with most stars belonging to the Galactic thick disk. Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar. 
\\ 
{\bf Odd-Z elements:}\\
The odd-Z elements Na and Al are also shown in  Fig.~\ref{alphael}. These elements are significantly enhanced 
\\
{\bf Fe-peak elements:}\\
XX
\\ 
{\bf Neutron capture elements:}\\
XX

%place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
